### 2021-11-15 input/proposal.tex
about issue

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
\TODO{Rework here.}
Figure~\ref{fig:problem} highlights such consistency issues with
dynamic partitions, even in contexts where \processes have FIFO links,
\ie where \processes receive the messages in the order of their
sending ($s_{pq}(m) \rightarrow s_{pq}(m') \implies r_q(m) \rightarrow
r_q(m')$). Both $a$ and $d$ add then delete their partition
concurrently. \Process~$c$ receives, delivers, and forwards
$\alpha_d^3$ followed by $\delta_d$. In the meantime, $b$ receives,
delivers, and forwards $\alpha_a^2$. In Figure~\ref{fig:problemC},
both $c$ and $d$ deliver the message about Partition $P_a$, for they
did not have any known partition at receipt time. On the contrary, $b$
delivers $\alpha_d^1$, for it improves its distance to a known
source. \Process~$b$ then blocks $a$'s removal notification
$\delta_a$. It never reaches $c$ nor $d$. Also, $c$ does not deliver
$\alpha_d$ and $\delta_d$ since it already delivered it. The system
converges to an inconsistent state where some \processes assume they
belong to a partition while it does not exist anymore. The system
needs to purge stale $\alpha$ messages that stop $\delta$ messages
from reaching nodes.

@@

A \process that removes its self-appointed status of source, or
detects a possible inconsistency, increments its local counter and
disseminates a delete notification message $\delta_{s, c}$
piggybacking its identifier $s$ and counter $c$. Any \process that
receives such delete notification deliver and forward it if their best
message contains the has-been source or detector associated to a lower
counter (see Line~\ref{line:ascast_delete}). This allows $\delta$
messages to quickly reach every downstream \process.

>>>>

Unfortunately, stale control information as stated in
Definition~\ref{def:lwo} may impair the propagation of both
\begin{inparaenum}[(i)]
\item notifications about actual sources, and
\item notifications about deleted partitions.
\end{inparaenum}
Figure~\ref{fig:problem} highlights such consistency issues with
dynamic partitions even in simple scenarios comprising three
\processes $a$, $b$, $c$ chained with FIFO links, \ie where \processes
receive the messages in the order of their sending ($s_{pq}(m)
\rightarrow s_{pq}(m') \implies r_q(m) \rightarrow r_q(m')$). In
Figure~\ref{fig:problemA}, both $a$ and $c$ become sources, sending
their respective notification message to $b$. In
Figure~\ref{fig:problemB} (bottom), both $a$ and $c$ delete their
partition while $b$ receives, delivers, and forwards $\alpha_a^2$. In
Figure~\ref{fig:problemC} (bottom), $b$ receives, delivers, and
forwards $\alpha_c^1$, for it improves its best partition. Then it
receives and discards $\delta_a$, for its best partition does not
match the deleted one. The bottom part of Figure~\ref{fig:problemD}
shows that eventually, $c$ stays in the deleted partition $P_a$ for
not having received $\delta_a$ that $b$ blocked earlier. As a
cascading effect, not only $c$ wrongfully believes that it belongs to
$a$'s partition when $a$ already deleted it, but it could contribute
to its inconsistency by blocking farther but up-to-date messages from
actual sources. Using local knowledge only, the system needs to purge
all stale messages to guarantee consistent partitioning.

@@

A \process that removes its self-appointed status of source, or
detects a possible inconsistency, increments its local counter and
disseminates a delete notification message $\delta_{s, c}$
piggybacking its identifier $s$ and counter $c$. Any \process that
receives such delete notification delivers and forwards it if its best
message contains the has-been source or detector associated to a lower
counter (see Line~\ref{line:ascast_delete}). This allows $\delta$
messages to quickly reach every downstream \process.
